Figure 4

### 2022-01-26 Figures/Figure4.Rmd
Fix style in Figure4.Rmd

prepare_table <- function(correlations, pvalues) {
  correlations %<>% select(...1, order(.[9,-1], decreasing = T))
pvalues %<>% dplyr::select(colnames(correlations))

longer_correlations <- correlations %>% pivot_longer(-1) %>% arrange(name)
longer_pvalues<- pvalues %>% pivot_longer(-1)

merged_all <- bind_cols(longer_correlations, longer_pvalues[, 3]) %>% dplyr::rename(cor=value...3, pvalue=value...4)
merged_all %>%
  mutate(text = case_when(
    is.na(pvalue) & is.na(cor) ~ str_c("NA"),
    is.na(pvalue) & (cor == 0) ~ str_c(cor, "\n"),
    pvalue >= 0.05 ~ str_c(cor),
    pvalue >= 0.01 & pvalue < 0.05 ~ str_c(cor, "\n*"),
    pvalue >= 0.001 & pvalue < 0.01 ~ str_c(cor, "\n**"),
    pvalue < 0.001 ~ str_c(cor, "\n***")
  )) %>% mutate(sorted_type = factor(...1, levels = unique(...1)))
}

@@

#ggsave("lymph_figure.pdf", dpi = "print", width = 210, height = 297, units = "mm", scale = 2)
```

>>>>

prepare_table <- function(correlations, pvalues) {
  correlations %<>% select(...1, order(.[9, -1], decreasing = T))
  pvalues %<>% dplyr::select(colnames(correlations))

  longer_correlations <- correlations %>%
    pivot_longer(-1) %>%
    arrange(name)
  longer_pvalues <- pvalues %>% pivot_longer(-1)

  merged_all <- bind_cols(longer_correlations, longer_pvalues[, 3]) %>% dplyr::rename(cor = value...3, pvalue = value...4)
  merged_all %>%
    mutate(text = case_when(
      is.na(pvalue) & is.na(cor) ~ str_c("NA"),
      is.na(pvalue) & (cor == 0) ~ str_c(cor, "\n"),
      pvalue >= 0.05 ~ str_c(cor),
      pvalue >= 0.01 & pvalue < 0.05 ~ str_c(cor, "\n*"),
      pvalue >= 0.001 & pvalue < 0.01 ~ str_c(cor, "\n**"),
      pvalue < 0.001 ~ str_c(cor, "\n***")
    )) %>%
    mutate(sorted_type = factor(...1, levels = unique(...1)))
}
```

@@

# ggsave("lymph_figure.pdf", dpi = "print", width = 210, height = 297, units = "mm", scale = 2)
```
